---
title: "Sign-ins"
code-fold: true
params:
    csv_dir: "private/csv"
    registration_fn: "registrations-2026.csv"
    presenters_fn: "presenters-2026.csv"
    signins_fn: "signins-2026.csv"
    sheets_fn: "Open Scholarship Bootcamp 2026: Registration (Responses)"
    reg_sheets_id: "1mM0rSuFS5_y2sQtU9AI9zm8kuOGeDzilJZdu1MUR8zk"
    psu_id: "rog1@psu.edu"
---

## About

This page documents and implements the data processing workflow for bootcamp electronic sign-ins via the Qualtrics link: <https://pennstate.qualtrics.com/jfe/form/SV_5vdpIekRnWpfsBo>

## Setup

We load some packages into memory for convenience.

```{r}
#| label: load-packages
suppressPackageStartupMessages(library('tidyverse'))
suppressPackageStartupMessages(library('ggplot2'))
suppressPackageStartupMessages(library('dplyr'))
suppressPackageStartupMessages(library('tidyr'))
suppressPackageStartupMessages(library('stringr'))
suppressPackageStartupMessages(library('lubridate'))
suppressPackageStartupMessages(library('janitor'))
```

## Gather

```{r}
#| label: import-data
#| message: false
#| 
x <- assertthat::is.string(params$csv_dir)
if (!dir.exists(params$csv_dir)) {
  message("Creating missing `include/csv/`.")
  dir.create(params$csv_dir)
}
x <- assertthat::is.writeable(params$csv_dir)

x <- assertthat::is.string(params$psu_id)
googlesheets4::gs4_auth(email = params$psu_id)

# Sign-ins
x <- assertthat::is.string(params$sheets_id)
signins <- googlesheets4::read_sheet(params$reg_sheets_id,
                                           sheet = "sign-ins")
x <- assertthat::assert_that(is_tibble(signins))

signins_full_fn <- file.path(params$csv_dir, params$signins_fn)
x <- assertthat::is.string(signins_full_fn)

# Registrations
registration_full_fn <- file.path(params$csv_dir, params$registration_fn)
x <- assertthat::is.string(registration_full_fn)
x <- assertthat::is.readable(registration_full_fn)

registrations <- readr::read_csv(file = registration_full_fn, show_col_types = FALSE)

# Presenters
presenters_full_fn <- file.path(params$csv_dir, params$presenters_fn)
x <- assertthat::is.string(presenters_full_fn)
x <- assertthat::is.readable(presenters_full_fn)

presenters <- readr::read_csv(file = presenters_full_fn, show_col_types = FALSE)
```

Check that we downloaded data.

```{r}
dim(signins)

dim(registrations)

dim(presenters)
```

## Clean

We need to clean the data file names.

```{r}
signins_clean <- janitor::clean_names(signins) |>
  dplyr::rename("signin_date" = "date") |>
  dplyr::mutate(name = paste0(first_name, " ", "last_name"))
```

```{r}
registrations_clean <- registrations |>
  dplyr::rename(
    timestamp = "Timestamp",
    attend_days = "Which days of the bootcamp will you attend?",
    name = "What is your name?",
    email = "Email Address",
    dept = "What is your department or unit?",
    position = "What is your current position?",
    comments = "Any comments?",
    dropped_out = "drop-out"
  )
```

```{r}
presenters_clean <- janitor::clean_names(presenters)
```

Show variable names prior to joining.

```{r}
names(signins_clean)
```

```{r}
names(registrations_clean)
```

```{r}
names(presenters_clean)
```

We have the following fields in common across the datasets: `name` & `email`.

```{r}
dfs <- list(signins_clean, registrations_clean, presenters_clean)

signins_join <- dfs |>
  purrr::reduce(left_join, by = c("email", "name"))
```

As of `r Sys.Date()`, we have had *n*=`r dim(signins_join)[1]` attendees and presenters sign in.

```{r}
#| label: save-signins-joined-csv
readr::write_csv(signins_join, file.path(params$csv_dir, "bootcamp-2026-signins.csv"))
```
