---
title: "Sign-ins"
code-fold: true
params:
    csv_dir: "private/csv"
    registration_fn: "registrations-2026-clean.csv"
    presenters_fn: "presenters-2026-clean.csv"
    signins_fn: "signins-2026.csv"
    sheets_fn: "Open Scholarship Bootcamp 2026: Registration (Responses)"
    reg_sheets_id: "1mM0rSuFS5_y2sQtU9AI9zm8kuOGeDzilJZdu1MUR8zk"
    psu_id: "rog1@psu.edu"
---

## About

This page documents and implements the data processing workflow for bootcamp electronic sign-ins via the Qualtrics link: <https://pennstate.qualtrics.com/jfe/form/SV_5vdpIekRnWpfsBo>

## Setup

We load some packages into memory for convenience.

```{r}
#| label: load-packages
suppressPackageStartupMessages(library('ggplot2'))
suppressPackageStartupMessages(library('tidyverse'))
```

## Gather

The registrations and presenters data are extracted as part of the [registrations](registration.qmd) workflow and saved as CSVs.
We'll import those.

The `sign-ins` tab contains the sign-ins data and must be retrieved from Google Forms.

```{r}
#| label: import-data
#| message: false
#| 
x <- assertthat::is.string(params$csv_dir)
if (!dir.exists(params$csv_dir)) {
  message("Creating missing `include/csv/`.")
  dir.create(params$csv_dir)
}
x <- assertthat::is.writeable(params$csv_dir)

x <- assertthat::is.string(params$psu_id)
googlesheets4::gs4_auth(email = params$psu_id)

# Sign-ins
x <- assertthat::is.string(params$sheets_id)
signins <- googlesheets4::read_sheet(params$reg_sheets_id,
                                           sheet = "sign-ins")
x <- assertthat::assert_that(is_tibble(signins))

signins_full_fn <- file.path(params$csv_dir, params$signins_fn)
x <- assertthat::is.string(signins_full_fn)

# Registrations
registration_full_fn <- file.path(params$csv_dir, params$registration_fn)
x <- assertthat::is.string(registration_full_fn)
x <- assertthat::is.readable(registration_full_fn)

# Import "cleaned" registrations file
registrations_clean <- readr::read_csv(file = registration_full_fn, show_col_types = FALSE)

# Presenters
presenters_full_fn <- file.path(params$csv_dir, params$presenters_fn)
x <- assertthat::is.string(presenters_full_fn)
x <- assertthat::is.readable(presenters_full_fn)

presenters <- readr::read_csv(file = presenters_full_fn, show_col_types = FALSE)
```

Check that we downloaded data.

```{r}
dim(signins)

dim(registrations_clean)

dim(presenters)
```

## Clean

We need to clean the data file names.

```{r}
signins_clean <- janitor::clean_names(signins) |>
  dplyr::rename("signin_date" = "date") |>
  dplyr::mutate(name = paste0(first_name, " ", last_name))
```

```{r}
presenters_clean <- janitor::clean_names(presenters)
```

Show variable names prior to joining.

```{r}
names(signins_clean)
```

```{r}
names(registrations_clean)
```

```{r}
names(presenters_clean)
```

Join `registrations_clean` and `presenters_clean`.

```{r}
people <- dplyr::full_join(registrations_clean, presenters_clean, by = NULL, copy = TRUE)
```

We have the following fields in common across the datasets: `name`, `email`.

```{r}
people_signed_in <- dplyr::full_join(signins_clean, people, by = NULL, copy = TRUE)
```

Modify `people_signed_in` to flag people who did not register in advance, but came to the workshop.

```{r}
people_signed_in <- people_signed_in |>
  dplyr::mutate(signin_noregister = if_else((!is.na(signin_date) &
                                               is.na(timestamp)), TRUE, FALSE),
                register_nosignin = if_else((is.na(signin_date) &
                                               !is.na(timestamp)), TRUE, FALSE))
```

```{r}
#| label: save-signins-joined-csv
readr::write_csv(people_signed_in, file.path(params$csv_dir, "bootcamp-2026-signins.csv"))
```

## Report

```{r}
mon_signins <- people_signed_in |>
  dplyr::filter(stringr::str_detect(as.character(signin_date), pattern = "2026-05-11"))

tue_signins <- people_signed_in |>
  dplyr::filter(stringr::str_detect(as.character(signin_date), "2026-05-12"))
```

### Monday, May 11

We had *n*=`r sum(!is.na(mon_signins$signin_date))` attendees and presenters sign in.
Of these, *n*=`r sum(mon_signins$signin_noregister)` attended but did not register in advance.
*N*=`r sum(mon_signins$register_nosignin)` registered or committed to present but did not sign-in.

Here is the distribution of units.

```{r}
#| label: fig-checkins-coll-mon
#| fig-cap: "Check-ins by college/unit on Monday, May 11"
 mon_signins |>
   dplyr::filter(!is.na(signin_date),
                 !is.na(college)) |>
   dplyr::count(college, sort = TRUE) |>
   dplyr::mutate(college = fct_reorder(college, n)) |>
   ggplot() +
   geom_bar(aes(x = college, y = n), fill = "#BF8226", stat = "identity") +
   scale_y_continuous(breaks = seq(2, 24, by = 2)) +
   theme(legend.position = "right") +
   theme(legend.title = element_blank()) +
   xlab("") +
   theme_classic() +
   coord_flip()
```

### Tuesday, May 12

We had *n*=`r sum(!is.na(tue_signins$signin_date))` attendees and presenters sign in.
Of these, *n*=`r sum(tue_signins$signin_noregister)` attended but did not register in advance.
*N*=`r sum(tue_signins$register_nosignin)` registered or committed to present but did not sign-in.

Here is the distribution of units.

```{r}
#| label: fig-checkins-coll-tue
#| fig-cap: "Check-ins by college/unit on Tuesday, May 12"
 tue_signins |>
   dplyr::filter(!is.na(signin_date),
                 !is.na(college)) |>
   dplyr::count(college, sort = TRUE) |>
   dplyr::mutate(college = fct_reorder(college, n)) |>
   ggplot() +
   geom_bar(aes(x = college, y = n), fill = "#BF8226", stat = "identity") +
   scale_y_continuous(breaks = seq(2, 24, by = 2)) +
   theme(legend.position = "right") +
   theme(legend.title = element_blank()) +
   xlab("") +
   theme_classic() +
   coord_flip()
```
